---
title: "Additional Environmental indices"
author: "Faustin Kambale"
date: "2024-10-16"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(purrr)
library(janitor)
library(forcats)
library(scales)
library(knitr)
library(kableExtra)
library(sjmisc)
library(likert)
library(writexl)
library(psych)
library(dplyr)
library(tm)
library(RColorBrewer)
library(wordcloud)

options(digits=2)
```

#working Directory

```{r setup, include=FALSE}
setwd("/Users/faustinkambale/Library/CloudStorage/OneDrive-DukeUniversity/Duke/Classes/Fall 2024/Bass Connextion/Duke-OIM/bass_southsudan/data")
```

#Insert Dataset

```{r}
OIM_dataset <- read.csv(file ='/Users/faustinkambale/Library/CloudStorage/OneDrive-DukeUniversity/Duke/Classes/Fall 2024/Bass Connextion/Duke-OIM/bass_southsudan/data/Bass_Team_Data_V2.csv', header=TRUE,skip=0)

df <- rename (OIM_dataset)
```

7) Environmental Fragility

All the answers are in a **scale of 0-1**, i.e. can have the following values: 0, 0.25, 0.5, 0.75, 1. The higher, the more fragile.

The higher, the more fragile.

Ex:
0 = Not severe at all 
0.25 = Not severe
0.50 = Somewhat severe
0.75 = Severe
1 = Extremely severe

## Index Questions

### Q11.10A Many people in South Sudan have experienced the following: too much rain, too little rain, temperatures that are too high, temperatures that are too low, pests and crop diseases, and deforestation and erosion. How severe would you say the impact of any of these experiences have been on your household income, on a scale from 1 to 5 where 1 means “not severe at all and 5 means “extremely severe?” {.tabset}

#### Entire sample

```{r Q11.10A, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  summarize(mean = mean(Q11.10A_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10A_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.10A_raw, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10A_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.10A_raw, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.10A_raw = factor(Q11.10A_raw)) %>%
  ggplot(aes(Q11.10A_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.10A_raw", y = "Number of respondents") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q11.10A by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q11.10A_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.10A_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.10A_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

#Interpretation 

1. High perception of severity : Most respondents perceive the environmental impact as either "Severe" or "Somewhat Severe," indicating a widespread recognition of environmental issues on income among households.
2. High Concern Level: Respondents selected "Severe". This suggests that many households feel the impact on income is significantly affecting them.
3. Moderate and Low Impact: Fewer respondents classify the impact as "Not Severe" or "Not Severe at all (no impact)," reflecting that a smaller portion of the population perceives a lower level of environmental impact.
4. Minimal Indifference: Very few respondents chose "Prefer not to answer," implying that most households have a clear stance on the issue, likely due to direct experiences with environmental challenges.
5. Impact perception by County : Bor South (0.73) and Rubkona (0.70) exhibit the highest mean responses (perception mean for the entire sample = 0.58), suggesting that households in these counties perceive a stronger environmental impact on income compared to other regions. 
Conclusion: Data show a significant distribution towards severity (with a negligible share of "no impact" respondents). This indicates that environmental issues are critical concerns in South Sudanese households income and people are aware of them. 

### Q11.10B And how severe would you say the impact of any of these experiences have been on your household food consumption?

#### Entire sample

```{r Q11.10B, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  summarize(mean = mean(Q11.10B_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10B_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.10B_raw, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10B_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.10B_raw, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.10B_raw = factor(Q11.10B_raw)) %>%
  ggplot(aes(Q11.10B_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.10B_raw", y = "Number of respondents") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q11.10B by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q11.10B_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.10B_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.10B_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

# Interpretation

1. High Severity Perception: The majority of respondents perceive the impact on food consumption as "Severe" or "Somewhat severe," indicating that food insecurity is a prominent concern among households.
2. Significant Extreme Impact: A notable proportion of households rate the impact as "Extremely severe," suggesting that many families are facing critical challenges related to food availability and consumption due to environmental challenges.
3. Minimal Indifference: Very few respondents chose "Prefer not to answer," implying that food consumption is a critical issue that most households are aware of and concerned about.
4.Above Average Impact: Rubkona (0.80) and Bor South (0.70) have mean responses well above the sample average (0.64), indicating that households in these counties perceive the impact on food consumption as particularly severe.
5. Counties with Lower Perceptions: Malakal (0.55) and Yei (0.56) report mean responses below the sample average, suggesting slightly lesser (but still notable) perceived impacts on food consumption in these areas.

Conclusion : The skew towards higher severity categories suggests that food-related environmental impact perceptions are not only prevalent but also pressing for most households in South Sudan.  Also, the mean responses above 0.55 for most counties reflect a general high perception of environmental impacts on food consumption by county.

### Q11.10C And how severe would you say the impact of any of these experiences have been on your household’s ability to choose where you live?

#### Entire sample

```{r Q11.10C, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  summarize(mean = mean(Q11.10C_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10C_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.10C_raw, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10C_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.10C_raw, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.10C_raw = factor(Q11.10C_raw)) %>%
  ggplot(aes(Q11.10C_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.10C_raw", y = "Number of respondents", title = "Household perception on where to live") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q11.10C by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q11.10C_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.10C_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.10C_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

##Interpretation

1. High Perception of Impact: Most respondents consider the environmental impact on "where to live" as either "Severe" or "Somewhat severe," indicating significant concerns about the impact on residential stability and choices.
2. Moderate to Extreme Impact Awareness: A large portion of households rate the impact as "Severe," showing that a majority of respondents are highly concerned about factors affecting their residential decisions.
3. Lower Levels of Non-Severity: Relatively fewer households perceive the impact as "Not severe" or "Not severe at all," indicating that environemtal impacts on residential issues are widely recognized as significant among respondents.
4. Above Average Impact: Rubkona (0.76) and Bor South (0.70) have mean responses significantly above the sample mean (0.59), suggesting that households in these counties face more severe challenges related to environmental impact on residential stability. Lainya (0.48) and Yei (0.49) show mean responses well below the sample mean, indicating that households in these areas perceive a comparatively lower environmental impact. 

conclusion : The distribution is skewed toward higher severity categories, highlighting the fact that environmental impacts on "where to live"  or living conditions are seen as pressing issues in the studied population. While the issue is widely recognized across different parts of the study area (most counties' mean is above 0.50), there is a significant regional disparities in how households perceive the impact on living conditions (highest mean in Rubkona (0.76) and the lowest in Lainya (0.48))

### Q11.10D And how severe would you say the impact of any of these experiences have been on your household’s health?

```{r Q11.10D, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  summarize(mean = mean(Q11.10D_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10D_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.10D_raw, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.10D_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.10D_raw, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.10D_raw = factor(Q11.10D_raw)) %>%
  ggplot(aes(Q11.10D_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.10D_raw", y = "Number of respondents", title = "Impact on household health") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q11.10D by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q11.10D_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.10D_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.10D_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

##Interpretation 

1. High Severity Perception: A significant portion of respondents rate the impact on household health as "Severe" or "Extremely severe," highlighting serious concerns regarding health conditions for households.
2. Prominent Health Concerns: The largest number of respondents identify the impact as "Severe," indicating that health-related issues are considered critical across many households. A relatively smaller group perceives the impact as "Somewhat severe," "Not severe," or "Not severe at all," showing that while there is some variance, the overall perception is skewed toward higher severity levels.
3. Above Average Impact: Rubkona (0.81) and Bor South (0.72) have mean responses significantly above the sample mean of 0.64, indicating that households in these counties perceive the impact on health as more severe than in Lainya (0.57) and Malakal (0.53) with mean responses below the sample average (lower but still notable perception).
4. Regional Variability: There is a clear variability across counties, with the highest mean perception in Rubkona (0.81) and the lowest in Malakal (0.53), highlighting differences in health impact experiences across different geographic locations.

Conclusion : The distribution of responses is heavily weighted toward more severe categories indicate that health impacts are seen as urgent problems.  Across the counties, the result show that most counties report mean responses above 0.57, reflecting that environmental impact perception on health is a widespread concern.

### Q11.11 Imagine that there was a flood coming to your town tomorrow. If you knew about this incoming flood before the water arrived, to what extent do you agree with the following statement: “I would be able to use this information to protect my household?”

```{r Q11.11, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  summarize(mean = mean(Q11.11_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.11_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.11_raw, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.11_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.11_raw, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.11_raw = factor(Q11.11_raw)) %>%
  ggplot(aes(Q11.11_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.11_raw", y = "Number of respondents", title = "Perception on Household Protection") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```
#### By county

```{r Q11.11 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q11.11_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.11_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.11_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

## Interpretation 

1. High Agreement: Most respondents either "Agree" or "Strongly agree" with the idea of protecting another household ahead of a hurricane, indicating a strong willingness among households to support each other during crises. However, the level of commitment varies among households reflected in the response category. 
2. Moderate Neutrality: A notable portion of respondents are "Neutral," suggesting that a significant number of households are either unsure or may be constrained in their ability to protect others in this circumstance.
3. Low Levels of Disagreement: Very few respondents "Disagree" or "Strongly disagree" with the notion of mutual protection, indicating that the concept of supporting others during a hurricane is generally accepted among the community.
4. Near or Above Average Perception: Some counties, like Pibor (0.45) and Lainya (0.39), have mean responses above the entire sample mean of 0.32, indicating relatively stronger agreement levels and possibly greater perceived capability for household mutual support in these areas.Bor South (0.16) and Rubkona (0.24) have the lowest mean responses, suggesting lower ability to protect neighboring household in the region.


Conclusion : This result suggest that protection  is both relevant and important to households in South Sudan. The mean response varies significantly, from a low of 0.16 in Bor South to a high of 0.45 in Pibor, reflecting differing levels of perceived ability or willingness to protect other households across counties. Despite regional differences, the overall lower scores suggest that households may feel limited in their ability to protect others, potentially due to their own vulnerability.

# Additinal questions on Environmental fragility 

##Q11.2 Are the water sources accessible to all households in the community?
  
  Yes = 1, No = 0

```{r}
df %>% 
  mutate(Q11.2 = ifelse((str_trim(Q11.2)) == "Yes", 1, 0))%>% # Convert to 1 and 0
  summarize(mean = mean(Q11.2, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)
 

df %>%
  group_by(Q11.2) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.2, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.2) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.2, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.2 = factor(Q11.2)) %>%
  ggplot(aes(Q11.2, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.2", y = "Number of respondents", title = "Water source access by household") +
  theme(axis.text.x = element_text(size = 13),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```
#### By county

```{r Q11.2 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  mutate(Q11.2 = ifelse((str_trim(Q11.2)) == "Yes", 1, 0))%>%
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q11.2, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.2) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.2, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

##Interpretation 

1. Majority Access: A high number of "Yes" responses in the graph suggests that water source access is relatively common among the surveyed households.There is access disparity as indicated by the "No" responses.This means there is a need for improved water infrastructure.
2. Minimal Indifference: Only a few respondents selected "Prefer not to answer," suggesting that most households have a clear understanding of their access to water sources, indicating the relevance of the question to their daily lives.
3. Above Average Access: Counties like Kajo-keji (0.85), Malakal (0.84), and Morobo (0.81) have mean responses well above the entire sample mean of 0.7, indicating better water source access in these areas, and Pibor (0.38) has a significantly lower mean response, suggesting a. lower water access. 

Conclusion:  While counties such as Lainya (0.64) and Bor South (0.62) have mean responses close to the overall sample mean suggesting moderate levels of water source access, the mean response of 0.38 in Pibor and 0.85 in Kajo-keji highlight significant disparities in water source access across different regions.


##Q11.3 What is the main reason water isn’t accessible to all households?
1.Distance, 2.Insecurity, 3.Quality of water, 4.Not enough water, 5. Non-functioning infrastructure, 6. Other: (please specify), -2. Prefer not to answer

```{r}
df %>%
  mutate(Q11.3 = case_when(
    Q11.3 == "Distance" ~ 1,
    Q11.3 == "Insecurity" ~ 2,
    Q11.3 == "Quality of water" ~ 3,
    Q11.3 == "Not enough water" ~ 4,
    Q11.3 == "Non-functioning infrastructure" ~ 5,
    Q11.3 == "Other" ~ 6,
    Q11.3 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_reponse = mean(Q11.3, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.3) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.3, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.3) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.3, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.3 = factor(Q11.3)) %>%
  ggplot(aes(Q11.3, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Reason for Water Absence", y = "Number of respondents", title = "Reasons for Lack of Water Access") +
  theme(axis.text.x = element_text(size = 13),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

#or a Pie chat 

df %>%
  group_by(Q11.3) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100,
         label = paste0(round(percentage, 1), "%")) %>%
  ggplot(aes(x = "", y = percentage, fill = Q11.3)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = label), color = "white", 
            position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Reasons for Lack of Water Access") +
  theme_void() +
  theme(legend.title = element_blank())

```
#### By county

```{r Q11.3 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.3 = case_when(
    Q11.3 == "Distance" ~ 1,
    Q11.3 == "Insecurity" ~ 2,
    Q11.3 == "Quality of water" ~ 3,
    Q11.3 == "Not enough water" ~ 4,
    Q11.3 == "Non-functioning infrastructure" ~ 5,
    Q11.3 == "Other" ~ 6,
    Q11.3 == "Prefer not to answer" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.3, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 6)")) %>%
  kable_styling(position = "left", full_width = F)


df %>%
  group_by(Q1.5_County, Q11.3) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.3, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

##Interpretation 

This question has a lot of NA which might bias the interpretation. However, we can extract some insights :
1. distance and water availability stand out as some of the barriers to water accessibility. This may suggest that geographical and availability factors prevent households from accessing water sources. 
2.Rubkona (3.5) and Wau (3.4) have mean responses well above the entire sample mean (2.5), indicating that households in these counties face more severe barriers related to water access, potentially due to greater distances or inadequate infrastructure. In contrast, Morobo (1.9) and Malakal (2.0) with lower mean responses suggest that these counties face less barriers to water access. 

## Q11.4 Is the water most people in your community drink safe for human consumption?
Yes = 1, No = 0,  -2. Prefer not to answer
```{r}
df %>% 
  mutate(Q11.4 = ifelse((str_trim(Q11.4)) == "Yes", 1, 0))%>% # Convert to 1 and 0
  summarize(mean = mean(Q11.4, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)
 
df %>%
  group_by(Q11.4) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.4, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.4) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.4, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.4 = factor(Q11.4)) %>%
  ggplot(aes(Q11.4, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.4", y = "Number of respondents", title = "Perception on water quality") +
  theme(axis.text.x = element_text(size = 13),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

#or a Pie chat 

df %>%
  group_by(Q11.4) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100,
         label = paste0(round(percentage, 1), "%")) %>%
  ggplot(aes(x = "", y = percentage, fill = Q11.4)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = label), color = "white", 
            position = position_stack(vjust = 0.5), size = 9) +
  labs(title = "Perseption on water quality") +
  theme_void() +
  theme(legend.title = element_blank())
```
#### By county

```{r Q11.4 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>% 
  mutate(Q11.4 = ifelse((str_trim(Q11.4)) == "Yes", 1, 0))%>%
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q11.4, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.4) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.4, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)
```

## Interpretation

1. Majority Positive Perception: Over half of the respondents (55.8%) have a positive perception of water quality, indicating that most households believe their water sources are of acceptable quality, but 43.7% of respondents report a negative perception, highlighting that water quality concerns are still prevalent among a substantial portion of the population.
2. Above Average Perception in Kajo-keji and Wau: Kajo-keji (0.86) and Wau (0.72) report the highest mean responses, indicating that households in these counties perceive better water quality compared to Morobo (0.32) and Yei (0.40) with mean responses well below the entire sample mean of 0.56, where water quality concerns are particularly significant.
3. Notable Disparity Across Counties: The range of mean responses, from 0.32 in Morobo to 0.86 in Kajo-keji, demonstrates significant regional disparities in water quality perceptions.


## Q11.5 Who in your household is responsible for collecting water? Select all that apply.
1. Male child, 2.Female child, 3. Adult woman, 4.Adult man,  -2. Prefer not to answer 

```{r}
#Clustering response by category 
df %>%
  group_by(Q11.5) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.5, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lcc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

# The multi-response matrix
df_matrix <- df %>%
  mutate(Male_Child = ifelse(grepl("Male child", Q11.5), 1, 0),
         Female_Child = ifelse(grepl("Female child", Q11.5), 1, 0),
         Adult_Woman = ifelse(grepl("Adult woman", Q11.5), 1, 0),
         Adult_Man = ifelse(grepl("Adult man", Q11.5), 1, 0)) %>%
  summarise(across(starts_with("Male_Child"):starts_with("Adult_Man"), sum)) %>%
  pivot_longer(cols = everything(), names_to = "Household_Member", values_to = "Count") 
df_matrix %>%
  kable(align = "lc", col.names = c("Household Member", "Count")) %>%
  kable_styling(position = "left", full_width = F)


# Plot a stacked bar chart
ggplot(df_matrix, aes(x = "", y = Count, fill = Household_Member)) +
  geom_bar(stat = "identity") +
  coord_polar("y") +
  labs(title = "Distribution of Water Collection Responsibilities by Household Member",
       x = NULL, y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())


# Plot flipped bar chart
ggplot(df_matrix, aes(x = reorder(Household_Member, -Count), y = Count, fill = Household_Member)) +
  geom_bar(stat = "identity") +
  labs(x = "Household Member Responsible for Water Collection", 
       y = "Count of Responses",
       title = "Responsibility for Water Collection by Household Member") +
  theme_minimal() +
  coord_flip() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE)
```
### by county

```{r}
#Descriptive table 
df %>%
  group_by(Q1.5_County, Q11.5) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.5, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)

#Short Matrix-Table 
df %>%
  mutate(Male_Child = ifelse(grepl("Male child", Q11.5), 1, 0),
         Female_Child = ifelse(grepl("Female child", Q11.5), 1, 0),
         Adult_Woman = ifelse(grepl("Adult woman", Q11.5), 1, 0),
         Adult_Man = ifelse(grepl("Adult man", Q11.5), 1, 0)) %>%
  group_by(Q1.5_County) %>%
  summarise(across(starts_with("Male_Child"):starts_with("Adult_Man"), sum, .names = "Count_{.col}")) %>%
  kable(align = "l", 
        col.names = c("County", "Male Child", "Female Child", "Adult Woman", "Adult Man")) %>%
  kable_styling(position = "left", full_width = F)

# Bar chart by county 

df_matrix_county <- df %>%
  mutate(Male_Child = ifelse(grepl("Male child", Q11.5), 1, 0),
         Female_Child = ifelse(grepl("Female child", Q11.5), 1, 0),
         Adult_Woman = ifelse(grepl("Adult woman", Q11.5), 1, 0),
         Adult_Man = ifelse(grepl("Adult man", Q11.5), 1, 0)) %>%
  group_by(Q1.5_County) %>%
  summarise(across(starts_with("Male_Child"):starts_with("Adult_Man"), sum)) %>%
  pivot_longer(cols = -Q1.5_County, names_to = "Household_Member", values_to = "Count")
ggplot(df_matrix_county, aes(x = reorder(Household_Member, Count), y = Count, fill = Household_Member)) +
  geom_bar(stat = "identity") +
  labs(x = "Household Member Responsible for Water Collection", 
       y = "Count of Responses",
       title = "Responsibility for Water Collection by Household Member and County") +
  theme_minimal() +
  coord_flip() +  # Flip for horizontal bars
  theme(axis.text.y = element_text(hjust = 1)) +
  guides(fill = FALSE) +
  facet_wrap(~ Q1.5_County, scales = "free_y")
```

##Interpretation 

1. Adult Women as Primary Collectors: The majority of responses indicate that adult women are primarily responsible for water collection across households followed by Female children, highlighting gendered roles in domestic water duties. This suggests that water collection duties often fall on both adult women and female children within households.
2. Limited Involvement of Men: Both adult men and male children have comparatively lower roles in water collection. This suggests that water collection is perceived largely as a women’s responsibility within households in South Soudan except in Kajo-keji, where there is a relatively higher involvement of both adult men (198) and male children (168) in sharing responsibility for water collection.
3. Rubkona's High Dependence on Adult Women: Rubkona has the highest number of responses indicating adult women (380) as the primary water collectors, with very low involvement from men. This suggests that water collection in Rubkona heavily relies on adult women.
4. Variation in Female Child Involvement: Counties like Malakal (326) and Bor South (303) have a high count for female children collecting water, suggesting that in these counties, water collection tasks are often assigned to younger female members of the household.

## Q11.7 On a scale from 1 through 5, where 1 is “strongly disagree” and 5 is “strongly agree,” how much do you agree with the following statements about your county’s experiences within the last 5 years?

All the answers are in a **scale of 1-5**, i.e. can have the following values: 1, 2, 3, 4, 5. The higher, the more agreement

Ex:
1 = Strongly disagree
2 = Disagree
3 = Neither agree nor disagree
4 = Agree
5 = Strongly agree
6 = Prefer not to respond

## Q11.7.1 In the last 5 years, the timing of the seasonal rains has changed

#### Entire sample

```{r Q11.7.1, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.1 = case_when(
    Q11.7.1 == "Strongly disagree" ~ 1,
    Q11.7.1 == "Disagree" ~ 2,
    Q11.7.1 == "Neither agree nor disagree" ~ 3,
    Q11.7.1 == "Agree" ~ 4,
    Q11.7.1 == "Strongly agree" ~ 5,
    Q11.7.1 == "Prefer not to respond" ~ 6,
    Q11.7.1 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.1, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.1) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.1, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.1) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.1, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.1 = factor(Q11.7.1)) %>%
  ggplot(aes(Q11.7.1, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.1", y = "Number of respondents", title = "Perception on seasonal rain change") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

# For a Pie chart

df %>%
  group_by(Q11.7.1) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.2 = factor(Q11.7.1)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.1)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Perception on seasonal rain change") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.1 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>%
  mutate(Q11.7.1 = case_when(
    Q11.7.1 == "Strongly disagree" ~ 1,
    Q11.7.1 == "Disagree" ~ 2,
    Q11.7.1 == "Neither agree nor disagree" ~ 3,
    Q11.7.1 == "Agree" ~ 4,
    Q11.7.1 == "Strongly agree" ~ 5,
    Q11.7.1 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.1, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.1) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.1, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

##Interpretation 

1. Strong Agreement on Rain Change: The majority of respondents either "Agree" or "Strongly agree" that there have been changes in seasonal rain patterns, indicating widespread awareness and recognition of climate shifts.Very few respondents "Disagree" or "Strongly disagree," reflecting a general consensus among households about the changing nature of seasonal rainfall.
2. Neutrality Among Some Respondents: A moderate number of households chose "Neither agree nor disagree," suggesting that some respondents are uncertain or have mixed experiences regarding changes in seasonal rain. 
3. Above Average Perception in Bor South: Bor South has the highest mean response (4.3) beyond the sample mean of 3.8, indicating that households in this county strongly perceive changes in seasonal rain patterns. In contrast, Pibor has the lowest mean response (3.5), indicating that households in this county are relatively less convinced about changes in rainfall patterns, though they still lean toward agreement.
4. Moderate Perception in Multiple Counties: Lainya (3.7), Morobo (3.7), and Rubkona (3.7) all have similar mean responses, showing a consistent but moderate acknowledgment of changing seasonal rainfall.

## Q11.7.2 In the last 5 years, water shortages in the dry season have become more frequent

#### Entire sample

```{r Q11.7.2, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.2 = case_when(
    Q11.7.2 == "Strongly disagree" ~ 1,
    Q11.7.2 == "Disagree" ~ 2,
    Q11.7.2 == "Neither agree nor disagree" ~ 3,
    Q11.7.2 == "Agree" ~ 4,
    Q11.7.2 == "Strongly agree" ~ 5,
    Q11.7.2 == "Prefer not to respond" ~ 6,
    Q11.7.2 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.2, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.2) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.2, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.2) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.2, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.2 = factor(Q11.7.2)) %>%
  ggplot(aes(Q11.7.2, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.2", y = "Number of respondents", title = "Perception on dry season frequency") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

#For a Pie chart 

df %>%
  group_by(Q11.7.2) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.2 = factor(Q11.7.2)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.2)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Perception on dry season frequency") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.2 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.2 = case_when(
    Q11.7.2 == "Strongly disagree" ~ 1,
    Q11.7.2 == "Disagree" ~ 2,
    Q11.7.2 == "Neither agree nor disagree" ~ 3,
    Q11.7.2 == "Agree" ~ 4,
    Q11.7.2 == "Strongly agree" ~ 5,
    Q11.7.2 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.2, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.2) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.2, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

## Interpretation

1. High agreement on increased dry season frequency: The majority of respondents "Agree" that the dry season frequency has increased.There is also a substantial number of respondents who "Strongly agree" with that perception, indicating a strong perception of prolonged dry spells among households widespread awareness of this climatic shift.
2. Moderate disagreement: A notable portion of respondents "Disagree," suggesting that some households may not have experienced an increase in dry season frequency or perceive it differently, potentially due to local variations in climate.
3.Regional perception : Bor South (3.8) and Wau (3.6) have mean responses above the sample mean of 3.5, indicating that households in these counties perceive more frequent dry seasons, Malakal (3.2) and Morobo (3.2) have the lowest mean responses, indicating that households in these counties perceive less change in dry season frequency or may be experiencing different climate dynamics.
4. Regional consistent perception: The similarity in mean responses for counties like Lainya (3.5), Kajo-keji (3.5), Pibor (3.5), and Rubkona (3.5) suggests a general consensus about increased dry season frequency, aligning closely with the sample mean.

## Q11.7.3 In the last 5 years, the diversity of wildlife has diminished

#### Entire sample

```{r Q11.7.3, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.3 = case_when(
    Q11.7.3 == "Strongly disagree" ~ 1,
    Q11.7.3 == "Disagree" ~ 2,
    Q11.7.3 == "Neither agree nor disagree" ~ 3,
    Q11.7.3 == "Agree" ~ 4,
    Q11.7.3 == "Strongly agree" ~ 5,
    Q11.7.3 == "Prefer not to respond" ~ 6,
    Q11.7.3 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.3, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.3) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.3, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.3) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.3, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.3 = factor(Q11.7.3)) %>%
  ggplot(aes(Q11.7.3, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.3", y = "Number of respondents", title = "Perception on diminishing wildlife diversity") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

#For a Pie chart 

df %>%
  group_by(Q11.7.3) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.3 = factor(Q11.7.3)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.3)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Perception on diminishing wildlife diversity") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.3 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.3 = case_when(
    Q11.7.3 == "Strongly disagree" ~ 1,
    Q11.7.3 == "Disagree" ~ 2,
    Q11.7.3 == "Neither agree nor disagree" ~ 3,
    Q11.7.3 == "Agree" ~ 4,
    Q11.7.3 == "Strongly agree" ~ 5,
    Q11.7.3 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.3, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.3) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.3, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

## Interpretation

1. High agreement on wildlife decline: The majority of respondents "Agree" that wildlife diversity has diminished. A considerable number of respondents also "Strongly agree"with the diminishing diversity, indicating a strong perception, awareness and concern among households of declining biodiversity over recent years.
2. Moderate disagreement and neutrality: There is a notable portion of respondents who "Disagree," and others "Neither agree nor disagree,". This may indicate that some households either have not observed significant changes or perceive the situation differently. Also, it may reflect uncertainty or mixed experiences regarding changes in wildlife diversity. 
3. Regional Perception: Bor South has the highest mean response (3.6), suggesting that households in this county perceive the most significant decline in wildlife diversity. Malakal (3.3), Kajo-keji (3.4), Rubkona (3.5), and Wau (3.4) have mean responses near the sample mean of 3.3, indicating that the perception of wildlife decline is relatively consistent across these regions.
4. Lower Perception : Pibor (3.0) and Yei (3.0) have the lowest mean responses, suggesting that households in these counties are less convinced of a significant decline in wildlife diversity.

##Q11.7.4 In the last 5 years, there has been an increase in urbanization, for example the construction of new buildings

#### Entire sample

```{r Q11.7.4, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.4 = case_when(
    Q11.7.4 == "Strongly disagree" ~ 1,
    Q11.7.4 == "Disagree" ~ 2,
    Q11.7.4 == "Neither agree nor disagree" ~ 3,
    Q11.7.4 == "Agree" ~ 4,
    Q11.7.4 == "Strongly agree" ~ 5,
    Q11.7.4 == "Prefer not to respond" ~ 6,
    Q11.7.4 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.4, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.4) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.4, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lcc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.4) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.4, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.4 = factor(Q11.7.4)) %>%
  ggplot(aes(Q11.7.4, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.4", y = "Number of respondents", title = "Perception on increase in urbanization") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

#For a Pie chart 

df %>%
  group_by(Q11.7.4) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.4 = factor(Q11.7.4)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.4)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Perception on increase in urbanization") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.4 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.4 = case_when(
    Q11.7.4 == "Strongly disagree" ~ 1,
    Q11.7.4 == "Disagree" ~ 2,
    Q11.7.4 == "Neither agree nor disagree" ~ 3,
    Q11.7.4 == "Agree" ~ 4,
    Q11.7.4 == "Strongly agree" ~ 5,
    Q11.7.4 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.4, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.4) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.4, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

##Interpretation

1. High agreement on urbanization increase: The majority of respondents "Agree" that there has been an increase in urbanization over the last five years, indicating a strong perception of expanding urban areas among households. others "Strongly agree," further emphasizing the perception that urbanization is rapidly progressing. However,a fair number of respondents chose "Neither agree nor disagree," indicating uncertainty or mixed experiences related to changes in urbanization
2. Considerable Disagreement: There is a substantial number of households that "Disagree" with the perception of increased urbanization, suggesting that some regions or communities may not have experienced significant urban growth.
3. Regional perception : Bor South (3.9), Rubkona (3.6), and Wau (3.6) have mean responses above the sample mean of 3.3, indicating that households in these counties perceive a stronger increase in urbanization compared to Morobo (2.7) and Yei (2.8) which have the lowest mean responses.
4. Regional moderate perception: Kajo-keji (3.2) and Lainya (3.2) have mean responses slightly below the sample mean, indicating moderate perceptions of urbanization that may vary across different parts of these counties.

##Q11.7.5 In the last 5 years, the land has become less fertile, such as from soil erosion

#### Entire sample

```{r Q11.7.5, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.5 = case_when(
    Q11.7.5 == "Strongly disagree" ~ 1,
    Q11.7.5 == "Disagree" ~ 2,
    Q11.7.5 == "Neither agree nor disagree" ~ 3,
    Q11.7.5 == "Agree" ~ 4,
    Q11.7.5 == "Strongly agree" ~ 5,
    Q11.7.5 == "Prefer not to respond" ~ 6,
    Q11.7.5 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.5, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.5) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.5, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.5) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.5, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.5 = factor(Q11.7.5)) %>%
  ggplot(aes(Q11.7.5, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.5", y = "Number of respondents", title = "Perception on land fertility decline") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

#For a Pie chart 

df %>%
  group_by(Q11.7.5) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.5 = factor(Q11.7.5)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.5)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Perception on land fertility decline") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.5 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

df %>%
  mutate(Q11.7.5 = case_when(
    Q11.7.5 == "Strongly disagree" ~ 1,
    Q11.7.5 == "Disagree" ~ 2,
    Q11.7.5 == "Neither agree nor disagree" ~ 3,
    Q11.7.5 == "Agree" ~ 4,
    Q11.7.5 == "Strongly agree" ~ 5,
    Q11.7.5 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.5, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.5) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.5, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

##Interpretation

1. High agreement on land fertility decline: The majority of respondents "Agree" that land fertility has declined, indicating a widespread perception of deteriorating soil productivity among households.Others "Strongly agree," reinforcing the perception that land fertility is diminishing.
2. Considerable disagreement: A notable portion of respondents "Disagree," indicating that some households do not perceive a significant decline in land fertility, which may reflect regional differences in soil quality or land management practices.
3. Regional perception: Bor South (3.6) and Rubkona (3.6) have mean responses above the sample mean of 3.3, indicating that households in these counties perceive a stronger decline in land fertility. In contrast, Pibor (2.9) and Yei (2.9) have the lowest mean responses, suggesting that households in these counties are less convinced of a significant decline in land fertility.
4. Regional matching perception: Kajo-keji (3.3) and Malakal (3.3) have mean responses that align with the sample mean, suggesting consistent matching perceptions of declining land fertility.

## Q11.7.6 In the last 5 years, deforestation has occurred, meaning that there has been cutting or other reductions in the size of forests

#### Entire sample

```{r Q11.7.6, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.6 = case_when(
    Q11.7.6 == "Strongly disagree" ~ 1,
    Q11.7.6 == "Disagree" ~ 2,
    Q11.7.6 == "Neither agree nor disagree" ~ 3,
    Q11.7.6 == "Agree" ~ 4,
    Q11.7.6 == "Strongly agree" ~ 5,
    Q11.7.6 == "Prefer not to respond" ~ 6,
    Q11.7.6 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.6, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.6) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.6, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.6) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.6, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.6 = factor(Q11.7.6)) %>%
  ggplot(aes(Q11.7.6, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.6", y = "Number of respondents", title = "Perception on deforestation") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

#For a Pie chart 

df %>%
  group_by(Q11.7.6) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.6 = factor(Q11.7.6)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.6)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Perception on deforestation") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.6 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.6 = case_when(
    Q11.7.6 == "Strongly disagree" ~ 1,
    Q11.7.6 == "Disagree" ~ 2,
    Q11.7.6 == "Neither agree nor disagree" ~ 3,
    Q11.7.6 == "Agree" ~ 4,
    Q11.7.6 == "Strongly agree" ~ 5,
    Q11.7.6 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.6, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.6) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.6, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

## Interpretation

1. High agreement on deforestation: The majority of respondents "Agree" that deforestation has increased in the last five years, indicating widespread recognition of this environmental issue among households.A large number of respondents also "Strongly agree" with the perception of increased deforestation, suggesting awareness and concern about deforestation among communities.However, 
2. Notable disagreement: Some respondents "Disagree," indicating that not all households have experienced or observed significant deforestation.
3. Moderate Neutral Responses: A significant number of households selected "Neither agree nor disagree," reflecting uncertainty or mixed experiences regarding deforestation trends over the last five years.
4. Regional high perception : Bor South (4.1) and Kajo-keji (3.9) have mean responses above the sample mean of 3.5, indicating stronger perceptions of increased deforestation. In contrast, Morobo (3.2), Pibor (3.0), and Yei (3.0) have the lowest mean responses, indicating that households in these counties perceive less severe deforestation or are less aware of its impacts.

### Q11.7.7 In the last 5 years, excessive grazing has caused damage to grassland.

#### Entire sample
```{r Q11.7.7, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.7 = case_when(
    Q11.7.7 == "Strongly disagree" ~ 1,
    Q11.7.7 == "Disagree" ~ 2,
    Q11.7.7 == "Neither agree nor disagree" ~ 3,
    Q11.7.7 == "Agree" ~ 4,
    Q11.7.7 == "Strongly agree" ~ 5,
    Q11.7.7 == "Prefer not to respond" ~ 6,
    Q11.7.7 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.7, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.7) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.7, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.7) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.7, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.7 = factor(Q11.7.7)) %>%
  ggplot(aes(Q11.7.7, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.7", y = "Number of respondents", title = "Perception of impact of grazing on grassland") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

#For a Pie chart 

df %>%
  group_by(Q11.7.7) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.7 = factor(Q11.7.7)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.7)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Perception of impact of grazing on grassland") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.7 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.7 = case_when(
    Q11.7.7 == "Strongly disagree" ~ 1,
    Q11.7.7 == "Disagree" ~ 2,
    Q11.7.7 == "Neither agree nor disagree" ~ 3,
    Q11.7.7 == "Agree" ~ 4,
    Q11.7.7 == "Strongly agree" ~ 5,
    Q11.7.7 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.7, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.7) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.7, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

## Interpretation

1. High agreement on grazing impact: The majority of respondents "Agree" that grazing has negatively impacted grasslands over the last five years. Also, a substantial number of respondents also "Strongly agree," suggesting a strong perception of environmental changes related to grazing practices, and awareness or concern among households about the impact of grazing on grassland health.
2. Considerable disagreement and neutrality: Some respondents "Disagree," and a fair number of respondents selected "Neither agree nor disagree," suggesting that not all households perceive grazing as a major threat to grassland, or uncertainty or mixed perceptions regarding the impact of grazing.
3. Regional perception: Rubkona has the highest mean response (3.6) compared to the overall sample mean of 3.4, indicating that households in this county perceive a stronger impact of grazing on grassland and Morobo (2.8) has the lowest mean response, indicating that households in this county perceive less impact of grazing on grassland.
4. Regional matching perception: Bor South (3.5), Kajo-keji (3.5), Lainya (3.5), and Wau (3.5) have mean responses close to the sample mean, suggesting consistent perceptions of grazing impact across these regions.

### Q11.7.8 In the last 5 years, the amount of waste left in the streets has increased.

#### Entire sample
```{r Q11.7.8, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}
df %>%
  mutate(Q11.7.8 = case_when(
    Q11.7.8 == "Strongly disagree" ~ 1,
    Q11.7.8 == "Disagree" ~ 2,
    Q11.7.8 == "Neither agree nor disagree" ~ 3,
    Q11.7.8 == "Agree" ~ 4,
    Q11.7.8 == "Strongly agree" ~ 5,
    Q11.7.8 == "Prefer not to respond" ~ 6,
    Q11.7.8 == "Prefer not to answer" ~ NA_real_
  )) %>%
  summarize(mean_response = mean(Q11.7.8, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.8) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q11.7.8, answers) %>%
  mutate(percentage = answers/sum(answers)) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q11.7.8) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q11.7.8, answers) %>%
  mutate(percentage = answers / sum(answers),
         Q11.7.8 = factor(Q11.7.8)) %>%
  ggplot(aes(Q11.7.8, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q11.7.8", y = "Number of respondents", title = "Percepion on increased waste") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip()

#For a Pie chart 

df %>%
  group_by(Q11.7.8) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q11.7.8 = factor(Q11.7.8)) %>%
  ggplot(aes(x = "", y = answers, fill = Q11.7.8)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = "Response",
       title = "Percepion on increased waste") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "white", size = 6)
```

#### By county

```{r Q11.7.8 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

# Convert Q11.7.8 to numeric
df %>%
  mutate(Q11.7.8 = case_when(
    Q11.7.8 == "Strongly disagree" ~ 1,
    Q11.7.8 == "Disagree" ~ 2,
    Q11.7.8 == "Neither agree nor disagree" ~ 3,
    Q11.7.8 == "Agree" ~ 4,
    Q11.7.8 == "Strongly agree" ~ 5,
    Q11.7.8 == "Prefer not to respond" ~ NA_real_
  )) %>%
  group_by(Q1.5_County) %>%
  summarize(mean_response = mean(Q11.7.8, na.rm = TRUE)) %>%
  kable(align = "lc", col.names = c("County", "Mean Response (1 to 5)")) %>%
  kable_styling(position = "left", full_width = F)

df %>%
  group_by(Q1.5_County, Q11.7.8) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers)) %>%
  ungroup() %>%
  select(Q1.5_County, Q11.7.8, answers, percentage) %>%
  kable(align = "llcc") %>%
  kable_styling(position = "left", full_width = F)
```

## Interpretation

1. High agreement on Waste Increase: The majority of respondents "Agree" that waste has increased over the last five years, indicating a strong perception of rising waste generation among households.A considerable number of respondents "Strongly agree," reflecting awareness and concern about waste management and its impacts.
2. Neutral and minimum indifference perceptions: While very few respondents selected "Prefer not to respond,", a fair number of respondents chose "Neither agree nor disagree," indicating that some households are uncertain or have mixed experiences regarding changes in waste generation. That small indifference can infer also that the issue of waste increase is relevant and prompts clear opinions among most households.
3. Regional perception : Bor South (3.6) and Kajo-keji (3.5) have mean responses above the sample mean of 3.2, indicating that households in these counties perceive a stronger increase in waste compared to Morobo (2.5) and Yei (2.8) which have the lowest mean responses, indicating that households in these counties perceive less of an increase in waste.
4. Regional matching and moderate perceptions: Malakal (3.4), Rubkona (3.5), and Wau (3.3) have mean responses that are close to or slightly above the sample mean, suggesting consistent perceptions of increased waste generation across these areas.in contrast, Pibor (3.0) and Lainya (3.0) have mean responses at the sample mean level, indicating mixed perceptions about waste increase. 